Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-07-25 2016-Weak-FH-Bisim/WeakBisim.tex
Proof of lemma 8 !

\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose1} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
	Suppose $j_0\in J$  and additionally:\\[-2ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\beta_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
		\ostate{(s_i')^{\, i\in L}}}
}
\quad\text{~~and~~}\quad
Q\models{\openrule
	{
		\set{\gamma},
		 \Pred_Q,  
		\Post_Q}
	{\ostate{s_{i}^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
		\ostate{(s'_{i})^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Let 
\begin{mathpar}
%J_Q=\displaystyle{\bigcup_{t=0}^nJ_{t}}
%\qquad
\Pred\,'=\Pred\land (\beta_{j_0}=\alpha_Q\land \Pred_Q) \quad\text{~~and~~}\quad
%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
\Post\,'=\Post\uplus\Post_Q
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\set{\gamma}\uplus\vis{\beta_j^{j\in J\setminus \{j_0\}}}, 
			\Pred\,',  \Post\,'
			 }
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}
\begin{proof}
By  Lemma \ref{lem-rel-OT-WOT} we can decompose the WOT of $Q$ into  a series of $k+1$ and $k'+1$ tau open transitions and an observable open transition:
\begin{mathpar}
\forall h\!\in\![0..k].Q\models\openrule
    {\set{\beta_{1h}},\Pred_{1h},\Post_{1h}   }
         {\ostate{{(s_{1h})}} \OTarrow {\tau} \ostate{{(s_{1(h+1)})}}}, \quad
Q\models{\openrule
	{
		\set{\beta_2},
		 \Pred_2,  
		\Post_2}
	{\ostate{s_{20}}\OTarrow {\alpha'_Q}
		\ostate{s_{21}}}
}, \\ \quad\text{~~and~~}\quad 
\forall h \in [0..k'].Q\models\openrule
         {
           \set{\beta_{3h}},\Pred_{3h}, \Post_{3h}}
         { \ostate{(s_{3h})} \OTarrow {\tau} \ostate{(s_{3(h+1)})}}
\end{mathpar}
such that\\ 
$\alpha_Q=\alpha'_Q\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$\\
$s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\
$\displaystyle{
\set{\gamma}=\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{j=h-1}^{0}\!\! \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=k}^{0}\Post_{1j}}} \dotcup}$\\
 $~~\hspace{1.8em}\displaystyle{ \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{j=h-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=k}^{0}\Post_{1j}} }}
\\
\Pred_Q=\bigwedge_{h=0}^{k}\!\big(\Pred_{1h}\subst{\bigotimes_{j=h-1}^{0}\Post_j^1}\big)\land \Pred_2\subst{\bigotimes_{h=k}^{0}\Post_{1h}}\land\\~\qquad\qquad \bigwedge_{h=0}^{k'}\!\Pred_{3h}\subst{\bigotimes_{j=h-1}^{0}{\Post_{3j}}\otimes{\Post_2}  \otimes\bigotimes_{h=k}^{0}\Post_{1h}}
\\
\Post_Q=\bigotimes_{h=k'}^{0}\Post_{3h}\otimes\Post_2\otimes\bigotimes_{j=k}^{0}\Post_{1j}
$

@@

Using Lemma \ref{lem-rel-OT-WOT}, from cases $(1)$, $(2)$ and $(3)$ we get: 
\[P[Q]_{j_0}\!\models		
\openrule
    {
\set{\gamma_c}, \Pred_c,
\Post_c}
         {\ostate{s_{10}\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha'} 
	\ostate{{{s'}^{i\in L}_{i}\uplus s_{3(k'+1)}}}}\] 
where\\
$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$
and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$.\\
$\displaystyle{
\set{\gamma_c}=\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{i=h-1}^{0}\!\! \Post_{1i} } }  \dotcup  \vis{({\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2})\subst{\bigotimes_{i=k}^{0}\Post_{1i}}} \dotcup}$ \\ 
$~~\hspace{1.8em}\displaystyle{\mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{i=h-1}^{0}\!\!\Post_{3i}\shortotimes\Post_2\shortotimes\bigotimes_{i=k}^{0}\Post_{1i}} }}$\\
$~~\hspace{0.6em}=\set{\gamma}\uplus\vis{\beta_j^{\in J\setminus \{j_0\}}} \quad$  because $\Post_{1j}$  does not act on variables of $\beta_j$.  \\
$\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_{1i}}\land
\left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\\displaystyle
\bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigotimes_{i=h-1}^{0}{\Post_{3i}}\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}
\end{array}
$\\
$\Post_c=\displaystyle{(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}$

Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\

@@

\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}). Suppose $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$ and additionally:\\[-2ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\gamma_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}\\
\text{~~and for all $t\in[0..n]$~~}
Q\models{\openrule
	{
		\gamma_{t j}^{j\in J_t},
		 \Pred_t,  
		\Post_t}
	{\ostate{s_{t i}^{i\in L_Q}} \OTWeakarrow {\alpha_t}
		\ostate{s_{(t+1) i}^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Let 
\begin{mathpar}
J_Q=\displaystyle{\bigcup_{t=0}^nJ_{t}}
\qquad
\Pred\,'=\Pred\land \bigwedge_{t=0}^{n}(\alpha_t=\beta_t\land \Pred_t)\bigotimes_{i=t-1}^{0}\Post_i
\\
\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
\Post\,'=\Post\uplus\bigotimes_{t=n}^{0}
		\Post_t
\\
\forall{i\in L_Q}.\,s_i=s_{0i} \text{\quad and \quad} \forall {i\in L_Q}.\,s'_i=s_{(n+1) i}
\end{mathpar}
\TODO{add posts to gammaj's above}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred\,',  \Post\,'
			 }
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}

\begin{proof} Suppose we have:
\begin{mathpar}
%\[
P\models{\openrule
	{
		\gamma_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$\forall p\!\in\![0..m_1].P\models\openrule
    {{\beta_{1pj}^{j\in J_{1p}}},\Pred_{1p},\Post_{1p}   }
         {\ostate{{(s_{1pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}} \wedge
P\models\openrule
         {\beta_{2j}^{j\in J_2},\Pred_2,\Post_2 }
         {\ostate{({s_{20i}})^{i\in L}} \OTarrow {\alpha'} \ostate{({s_{21i}})^{i\in L}}}
\wedge\\
\forall p \in [0..m_2].P\models\openrule
         {
           \beta_{3pj}^{j\in J_{3p}},\Pred_{3p}, \Post_{3p}}
         { \ostate{(s_{3pi})^{i\in L}} \OTarrow {\tau} \ostate{(s_{3(p+1)i})^{i\in L}}}$ 
\\
where for all $i\in L$:\\
$s_i=s_{10 i} \wedge s_{1(m_1+1) i}=s_{20i} \wedge  s_{21i}= s_{30 i} \wedge s_{3(m_2+1) i}=s'_i$\\
\[\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}\]
\[\displaystyle{
\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{1p}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\Post_{1j}}}}\]
\begin{equation*}
\begin{split}
\Pred&=\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred^2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}
\\
\Post&=\bigotimes_{p=m_2}^{0}\Post_{3p}\otimes\Post_2\otimes\bigotimes_{j=m_1}^{0}\Post_{1j}
\end{split}
\end{equation*}

@@

We have, by definition of $n_i$ and $n'_i$:
\begin{equation*}
\begin{split}
\forall{i\in[0..m-1]}.],&\beta_{1 n_i j_0}\subst{\bigotimes_{j=n_i-1}^{0} \Post_{1j} }=\beta_i\\ 
&
\beta_{2 j_0}\subst{\bigotimes_{j=m_1}^{0} \Post_{1j} }=\beta_m\\ 
\forall{i\in[m+1..n]}.],&\beta_{3 n'_i j_0}\subst{\bigotimes_{j=n'i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\Post_{1j}}=\beta_i\\ 
\end{split}\end{equation*}

Now, we compose OTs for each of the case above (OTs of $P$)':
\begin{enumerate}
\item $p\in [0..m_1]$. Either there is $i$ such that $p=n_i$, and thus $\beta_i=\beta_{1 p j_0}$. In this case by Lemma~\ref{lem-Weakcompose1}, we have:

Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\set{\beta'_{1p}}, 
			\Pred_{1p}\,',  \Post_{1p}\,'
			 }
		{\ostate{s_{1pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTWeakarrow {\tau}
			\ostate{s_{1(p+1)j}^{\, j\in L}\uplus s_{(i+1)j}^{j\in L_Q} } }
	}
	\]
with 
\begin{mathpar}
\set{\beta'_{1p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{1pj}^{j\in J_{1p}\setminus \{j_0\}}}\\
\Pred\,'_{1p}=\Pred_{1p}\land (\beta_{1pj_0}=\alpha_i\land \Pred_i)
\\
%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
\Post\,'_{1p}=\Post_{1p}\uplus\Post_i
\end{mathpar}

Or $j_0\not \in \dom(\beta_{1 p})$ and $Q$ does not move in the composed reduction. In this case there is no $i$ such that $p=n_i$, but there is $i$ such that $p\in]n_i .. n_{i+1}[$, and
\[P[Q]_{j_0} \models\openrule
    {\set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
         {\ostate{s_{1pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTarrow {\tau} \ostate{s_{1(p+1)j}^{j\in L}\uplus s_{ij}^{j\in L_Q}}}
\]
and thus we also have a weak OT by definition:
\[P[Q]_{j_0} \models\openrule
    {\set{\beta'_{1p}},\Pred\,'_{1p},\Post\,'_{1p}   }
         {\ostate{s_{1pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTWeakarrow {\tau} \ostate{s_{1(p+1)j}^{j\in L}\uplus s_{ij}^{j\in L_Q}}}
\]
with 
\begin{mathpar}
\set{\beta'_{1p}}=\set{\beta_{1p}}\\
\Pred_{1p}\,'=\Pred_{1p}\\
\Post_{1p}\,'=\Post_{1p}
\end{mathpar}

\item idem for the middle OT with label $\alpha$:
\[P[Q]_{j_0}\models\openrule
         {	\gamma_{m j}^{j\in J_m}\uplus\vis{\beta_{2j}^{j\in J_2\setminus \{j_0\}}},\Pred_2',\Post_2' }
         {\ostate{{s_{20j}}^{j\in L}\uplus s_{mj}^{j\in L_Q}}\OTarrow {\alpha'} \ostate{{(s_{21j})}^{j\in L}\uplus s_{(m+1)j}^{j\in L_Q}}}\]
with 
\begin{mathpar}
\Pred_{2}\,'=\Pred_{2}\land (\beta_{2j_0}=\alpha_m\land \Pred_m)
\\
%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
\Post_{2}\,'=\Post_{2}\uplus\Post_m
\end{mathpar}

\item and for the last $\tau$ OTs:
for $p\in [0..m_2]$. Either there is $i$ such that $p=n'_i$, and thus $\beta_i=\beta_{1 p j_0}$. In this case by Lemma~\ref{lem-Weakcompose1}, we have:

>>>>

\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose1} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
	Suppose $j_0\in J$  and additionally:\\[-2ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\beta_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {\alpha}
		\ostate{(s_i')^{\, i\in L}}}
}
\quad\text{~~and~~}\quad
Q\models{\openrule
	{
		\set{\gamma},
		 \Pred_Q,  
		\Post_Q}
	{\ostate{s_{i}^{i\in L_Q}} \OTWeakarrow {\alpha_Q}
		\ostate{(s'_{i})^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Let 
\begin{mathpar}
%J_Q=\displaystyle{\bigcup_{t=0}^nJ_{t}}
%\qquad
\Pred\,'=\Pred\land (\beta_{j_0}=\alpha_Q\land \Pred_Q) \quad\text{~~and~~}\quad
%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
\Post\,'=\Post\uplus\Post_Q
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\set{\gamma}\uplus\vis{\beta_j^{j\in J\setminus \{j_0\}}}, 
			\Pred\,',  \Post\,'
			 }
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
			\ostate{(s_i')^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}
\begin{proof}
By  Lemma \ref{lem-rel-OT-WOT} we can decompose the WOT of $Q$ into  a series of $k+1$ and $k'+1$ tau open transitions and an observable open transition:
\begin{mathpar}
\forall h\!\in\![0..k].Q\models\openrule
    {\set{\beta_{1h}},\Pred_{1h},\Post_{1h}   }
         {\ostate{{(s_{1h})}} \OTarrow {\tau} \ostate{{(s_{1(h+1)})}}}, \quad
Q\models{\openrule
	{
		\set{\beta_2},
		 \Pred_2,  
		\Post_2}
	{\ostate{s_{20}}\OTarrow {\alpha'_Q}
		\ostate{s_{21}}}
}, \\ \quad\text{~~and~~}\quad 
\forall h \in [0..k'].Q\models\openrule
         {
           \set{\beta_{3h}},\Pred_{3h}, \Post_{3h}}
         { \ostate{(s_{3h})} \OTarrow {\tau} \ostate{(s_{3(h+1)})}}
\end{mathpar}
such that\\ 
{\footnotesize $\alpha_Q=\alpha'_Q\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$\\
$s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\
$\displaystyle{
\set{\gamma}=\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{j=h-1}^{0}\!\! \Post_{1j} } }  \dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=k}^{0}\Post_{1j}}} \dotcup}$\\
 $~~\hspace{1.8em}\displaystyle{ \mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{j=h-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=k}^{0}\Post_{1j}} }}
\\
\Pred_Q=\bigwedge_{h=0}^{k}\!\big(\Pred_{1h}\subst{\bigotimes_{j=h-1}^{0}\Post_j^1}\big)\land \Pred_2\subst{\bigotimes_{h=k}^{0}\Post_{1h}}\land\\~\qquad\qquad \bigwedge_{h=0}^{k'}\!\Pred_{3h}\subst{\bigotimes_{j=h-1}^{0}{\Post_{3j}}\otimes{\Post_2}  \otimes\bigotimes_{h=k}^{0}\Post_{1h}}
\\
\Post_Q=\bigotimes_{h=k'}^{0}\Post_{3h}\otimes\Post_2\otimes\bigotimes_{j=k}^{0}\Post_{1j}
$
}
\begin{enumerate}

@@

Using Lemma \ref{lem-rel-OT-WOT}, from cases $(1)$, $(2)$ and $(3)$ we get: 
\[P[Q]_{j_0}\!\models		
\openrule
    {
\set{\gamma_c}, \Pred_c,
\Post_c}
         {\ostate{s_{10}\uplus s^{i\in L}_{i}} \OTWeakarrow {\alpha'} 
	\ostate{{{s'}^{i\in L}_{i}\uplus s_{3(k'+1)}}}}\] 
where\\
$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=k}^{0}\Post_{1j}}}$
and $\alpha=\alpha'$  because $\Post_{1j}$ acts on variables of $Q$ and $\alpha$ contains only variables of $P$.\\
{\footnotesize $\displaystyle{
\set{\gamma_c}=\mybigdotcup_{h=0}^k \vis{\set{\beta_{1h}}\subst{\bigotimes_{i=h-1}^{0}\!\! \Post_{1i} } }  \dotcup  \vis{({\beta_{j}}^{(j\in J\setminus\{j_0\})} \uplus \set{\beta_2})\subst{\bigotimes_{i=k}^{0}\Post_{1i}}} \dotcup}$ \\ 
$~~\hspace{1.8em}\displaystyle{\mybigdotcup_{h=0}^{k'} \vis{\set{\beta_{3h}} \subst{\bigotimes_{i=h-1}^{0}\!\!\Post_{3i}\shortotimes\Post_2\shortotimes\bigotimes_{i=k}^{0}\Post_{1i}} }}$\\
$~~\hspace{0.6em}=\set{\gamma}\uplus\vis{\beta_j^{\in J\setminus \{j_0\}}} \quad$  because $\Post_{1j}$  does not act on variables of $\beta_j$.  \\
$\Pred_c=\begin{array}[t]{l}\displaystyle\bigwedge_{h=0}^k{\Pred_{1h}}\subst{\bigotimes_{i=h-1}^{0}\Post_{1i}}\land
\left(Pred\land\Pred_2\land \alpha'_Q=\beta_{j_0 }\right)\subst{\bigotimes_{i=k}^{0}{\Post_{1i}}}\land\\\displaystyle
\bigwedge_{h=0}^{k'}{\Pred_{3h}}\subst{\bigotimes_{i=h-1}^{0}{\Post_{3i}}\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}
\end{array}
$\\
$\Post_c=\displaystyle{(\bigotimes_{i=k'}^{0}{\Post_{3i}})\shortotimes({\Post\uplus \Post_2})\shortotimes\bigotimes_{i=k}^{0}{\Post_{1i}}}$
}
Note that we have $s_i^{i\in L_Q}=s_{10} \wedge s_{1(k+1) i}=s_{20} \wedge  s_{21}= s_{30} \wedge s_{3(k'+1) i}={s'}_i^{i\in L_Q}$\\

@@

\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}). Suppose $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$ and additionally:\\[-2ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\gamma_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}\\
\text{~~and for all $t\in[0..n]$~~}
Q\models{\openrule
	{
		\gamma_{t j}^{j\in J_t},
		 \Pred_t,  
		\Post_t}
	{\ostate{s_{t i}^{i\in L_Q}} \OTWeakarrow {\alpha_t}
		\ostate{s_{(t+1) i}^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Let 
\begin{mathpar}
J_Q=\displaystyle{\bigcup_{t=0}^nJ_{t}}
\qquad
\Pred\,'=\Pred\land \bigwedge_{t=0}^{n}(\alpha_t=\beta_t\land \Pred_t)\bigotimes_{i=t-1}^{0}\Post_i
\\
\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}\subst{\bigotimes_{k=t}^{0}{\Post_k}}}\text{\quad and\quad}
\Post\,'=\Post\uplus\bigotimes_{t=n}^{0}
		\Post_t
\\
\forall{i\in L_Q}.\,s_i=s_{0i} \text{\quad and \quad} \forall {i\in L_Q}.\,s'_i=s_{(n+1) i}
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred\,',  \Post\,'
			 }
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}

\begin{proof} Suppose we have:
\begin{mathpar}
%\[
P\models{\openrule
	{
		\gamma_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
\begin{mathpar}
\forall p\!\in\![0..m_1].P\models\openrule
    {{\beta_{1pj}^{j\in J_{1p}}},\Pred_{1p},\Post_{1p}   }
         {\ostate{{(s_{1pi})}^{i\in L}} \OTarrow {\tau} \ostate{{(s_{1(p+1)i})}^{i\in L}}} \\
P\models\openrule
         {\beta_{2j}^{j\in J_2},\Pred_2,\Post_2 }
         {\ostate{({s_{20i}})^{i\in L}} \OTarrow {\alpha'} \ostate{({s_{21i}})^{i\in L}}}
\\
\forall p \in [0..m_2].P\models\openrule
         {
           \beta_{3pj}^{j\in J_{3p}},\Pred_{3p}, \Post_{3p}}
         { \ostate{(s_{3pi})^{i\in L}} \OTarrow {\tau} \ostate{(s_{3(p+1)i})^{i\in L}}}
\end{mathpar}
where for all $i\in L$:\\
$s_i=s_{10 i} \wedge s_{1(m_1+1) i}=s_{20i} \wedge  s_{21i}= s_{30 i} \wedge s_{3(m_2+1) i}=s'_i$\\
\[\alpha=\alpha'\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}}\]
\begin{multline*}
\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{{\beta_{1ij}^{j\in J_{1p}}}\subst{\bigotimes_{j=i-1}^{0} \Post_{1j} } }  \dotcup  \vis{{\beta_{2j}^{j\in J_{2}}}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \\
\dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta_{3ij}^{j\in J_{1p}} \subst{\bigotimes_{j=i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\Post_{1j}}}
\end{multline*}
\begin{multline*}
\Pred=\bigwedge_{p=0}^{m_1}\!\big(\Pred_{1p}\subst{\bigotimes_{j=p-1}^{0}\Post_{1j}}\big)\land\Pred^2\subst{\bigotimes_{p=m_1}^{0}\Post_{1p}}\land\\ \bigwedge_{p=0}^{m_2}\!\Pred_{3p}\subst{\bigotimes_{j=p-1}^{0}\Post_{3j}\otimes\Post_2 \otimes\bigotimes_{p=m_1}^{0}\Post_{1p}}
\end{multline*}
\begin{equation*}
\begin{split}
\Post&=\bigotimes_{p=m_2}^{0}\Post_{3p}\otimes\Post_2\otimes\bigotimes_{j=m_1}^{0}\Post_{1j}
\end{split}
\end{equation*}

@@

We have, by definition of $n_i$ and $n'_i$:
\begin{equation*}
\begin{split}
\forall{i\in[0..m-1]},&\beta_{1 n_i j_0}\subst{\bigotimes_{j=n_i-1}^{0} \Post_{1j} }=\beta_i\\ 
&
\beta_{2 j_0}\subst{\bigotimes_{j=m_1}^{0} \Post_{1j} }=\beta_m\\ 
\forall{i\in[m+1..n]},&\beta_{3 n'_i j_0}\subst{\bigotimes_{j=n'i-1}^{0}\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\Post_{1j}}=\beta_i\\ 
\end{split}\end{equation*}

Now, we compose OTs for each of the case above (OTs of $P$)':
\begin{enumerate}
\item $p\in [0..m_1]$. Either there is $i$ such that $p=n_i$, and thus $\beta_i$ and $\beta_{1 p j_0}$ are defined. In this case by Lemma~\ref{lem-Weakcompose1}, we have:

Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\set{\gamma'_{1p}}, 
			\Pred_{1p}\,',  \Post_{1p}\,'
			 }
		{\ostate{s_{1pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTWeakarrow {\tau}
			\ostate{s_{1(p+1)j}^{\, j\in L}\uplus s_{(i+1)j}^{j\in L_Q} } }
	}
	\]
with 
\begin{mathpar}
\set{\gamma'_{1p}}=\gamma_{i j}^{j\in J_i}\uplus\vis{\beta_{1pj}^{j\in J_{1p}\setminus \{j_0\}}}\\
\Pred\,'_{1p}=\Pred_{1p}\land (\beta_{1pj_0}=\alpha_i\land \Pred_i)
\\
%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
\Post\,'_{1p}=\Post_{1p}\uplus\Post_i
\end{mathpar}

Or $j_0\not \in \dom(\beta_{1 p})$ and $Q$ does not move in the composed reduction. In this case there is no $i$ such that $p=n_i$, but there is $i$ such that $p\in]n_i .. n_{i+1}[$, and
\[P[Q]_{j_0} \models\openrule
    {\set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
         {\ostate{s_{1pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTarrow {\tau} \ostate{s_{1(p+1)j}^{j\in L}\uplus s_{ij}^{j\in L_Q}}}
\]
and thus we also have a weak OT by definition:
\[P[Q]_{j_0} \models\openrule
    {\set{\gamma'_{1p}},\Pred\,'_{1p},\Post\,'_{1p}   }
         {\ostate{s_{1pj}^{j\in L}\uplus s_{ij}^{j\in L_Q}} \OTWeakarrow {\tau} \ostate{s_{1(p+1)j}^{j\in L}\uplus s_{ij}^{j\in L_Q}}}
\]
with 
\begin{mathpar}
\set{\gamma'_{1p}}=\set{\vis{\beta_{1p}}}\\
\Pred\,'_{1p}=\Pred_{1p}\\
\Post\,'_{1p}=\Post_{1p}
\end{mathpar}

\item idem for the middle OT with label $\alpha$:
\[P[Q]_{j_0}\models\openrule
         {	\set{\gamma'_2},\Pred_2',\Post_2' }
         {\ostate{{s_{20j}}^{j\in L}\uplus s_{mj}^{j\in L_Q}}\OTWeakarrow {\alpha'} \ostate{{(s_{21j})}^{j\in L}\uplus s_{(m+1)j}^{j\in L_Q}}}\]
with 
\begin{mathpar}
\set{\gamma'_2}=\gamma_{m j}^{j\in J_m}\uplus\vis{\beta_{2j}^{j\in J_2\setminus \{j_0\}}}\\
\Pred\,'_{2}=\Pred_{2}\land (\beta_{2j_0}=\alpha_m\land \Pred_m)
\\
%\forall j\in J_t,\,\gamma_j= \displaystyle{\mybigdotcup_{t=0}^n \gamma_{t j}}\text{\quad and\quad}
\Post\,'_{2}=\Post_{2}\uplus\Post_m
\end{mathpar}

\item and for the last $\tau$ OTs:
for $p\in [0..m_2]$. Either there is $i$ such that $p=n'_i$, and thus $\beta_i$ and $\beta_{1 p j_0}$ are defined. In this case by Lemma~\ref{lem-Weakcompose1}, we have:
